{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2015-03-03 brains-protocol.tex
Fix a few numbers after new filtering

\rk{fix}

Manual inspection of this dataset revealed that it contains a significant number of everyday language quotations (such as ``it was much better than I expected'', ``did that just happen'', as well as many simple expletive-based sentences).
Their presence is largely due to random variations around a casual expression, while we are interested in transformations of news-related quotes causally linked to an original, identifiable utterance.
We thus filter out all clusters lasting more than 80 days, and all quotes less than 5 words long %\seb{it is asymmetrical...}
 (as well as quotes not written in English).
% New filtering: 1051 substitutions out of 6172 mined. 45749 clusters. -- correct text with numbers and for new figures.
We eventually keep 19,621 clusters (out of 71,568; i.e. 27.4\%), containing a total of 60,246 unique quotes (out of 310,457; i.e. 19.4\%) making up $\sim$838k occurrences (out of 8.12m, i.e. 10.3\%).
The significantly larger loss in occurrences indicates that, on average, the clusters we lose contain more occurrences than those we keep, which is expected for everyday language utterances.\footnote{While we lose some real event-related utterances because of their presence in clusters lasting more than 80 days (such as ``the terrorists have used automatic weapons and in some places grenades have been lobbed the encounters are still going on and we are trying to overpower them''), we contend that the use of the unfiltered dataset would strongly jeopardize results related to linguistic evolution or information diffusion. We manually checked on a subsample of clusters that a large proportion of remaining quotes seem to be relevant, while filtered quotes are essentially irrelevant.\rk{fix}}

@@

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/feature_susceptibilities.png}
    \caption{\textbf{Substitution susceptibility:} \rk{fix} average susceptibility to substitution vs. average feature value of a candidate word for substitution, with 95\% asymptotic confidence intervals.
    The heatmap on the lower-right shows the joint effect of Age of acquisition and Number of phonemes on susceptibility, averaged over the respective single-variable ranges, with sample size (word numbers) in parentheses.
    Without the rather non-significant cells (11 words or less), the heatmap shows no specific trend in one direction or the other.}
    \label{fig:feature-susceptibilities}
\end{figure*}
\medskip
\rk{fix} Results for this measure are gathered in Fig.~\ref{fig:feature-susceptibilities}. They first show an obvious strong effect of Word frequency: the more frequent a word, the less likely it is to attract substitutions.
Indeed, susceptibility goes from nearly 0.4 for low-frequency words down to 0 for very high-frequency words.
To make things clear, this value of 0.4 means that low-frequency words, when present in a quote undergoing a substitution, are the ones being substituted 40\% of the time on average.

\rk{fix} The other features --- Age of acquisition, Number of phonemes, Clustering coefficient and Number of synonyms --- do not seem to exhibit any particularly significant effect on susceptibility.
For each of these features, it is indeed possible to draw a constant line which always remains within the respective confidence intervals.
If these variables have an effect, it is by no means as strong as it is for Word frequency.
This is remarkably clear for Clustering coefficient and Number of synonyms, where susceptibility values remain within quite small intervals (respectively [0.09-0.13] and [0.11-0.15]).
We may notice a somewhat marked effect for the highest values of Age of acquisition and Number of phonemes, where the mean susceptibility is almost twice as high as in the rest (respectively 0.19 vs 0.13, and 0.21 vs 0.12).
Keeping in mind the poor statistical significance of this effect, we could still suggest that the longest words and words learned late are more susceptible to substitution.
To further examine this phenomenon, we plotted the two-dimensional map of susceptibility values for these two features (see heatmap at the bottom right of Fig.~\ref{fig:feature-susceptibilities}).
We see that outlier values (the two darkest cells) are both due to cells where the number of items is only slightly above the significance threshold (11 items, while we decided to cut at 10).
If we focus on cells based on at least several dozens of words, values range from 0.11 to 0.22 with little obvious regularity, making it hard to draw any conclusion as regards the direction of an effect.
This confirms the fact that the slight late increases observed for Age of acquisition and Number of phonemes are rather non-significant.

@@

\rk{fix} All in all, apart from Word frequency and despite some tendencies these results do not allow us to conclude either to a marked effect %or to no effect 
of the selected psycholinguistic features on substitution susceptibility.
We may therefore globally assume that substitution targets are chosen in a more or less uniform way with respect to these features.

>>>>

Manual inspection of this dataset revealed that it contains a significant number of everyday language quotations (such as ``it was much better than I expected'', ``did that just happen'', as well as many simple expletive-based sentences).
Their presence is largely due to random variations around a casual expression, while we are interested in transformations of news-related quotes causally linked to an original, identifiable utterance.
\TB{We thus filter out all quotes less than 5 words long or lasting more than 80 days} %\seb{it is asymmetrical...}
 (as well as quotes not written in English).
\TB{If an entire cluster still lasts more than 80 days after this screening (because of short-lived but unrelated quotes far apart in time), we also filter it out.}
% New filtering: 1051 substitutions out of 6172 mined. 45749 clusters. -- correct text with numbers and for new figures.
We eventually keep 45,749 clusters (out of 71,568; i.e. 63.9\%), containing a total of 127,778 unique quotes (out of 310,457; i.e. 41.2\%) making up $\sim$2.43m occurrences (out of 8.16m, i.e. 29.8\%).
The significantly larger loss in occurrences indicates that, on average, the clusters we lose contain more occurrences than those we keep, which is expected for everyday language utterances.\footnote{While we lose some real event-related utterances because of their presence in clusters lasting more than 80 days (such as \TB{``the city is tired of me and the organization and i have run our course together''}), we contend that the use of the unfiltered dataset would strongly jeopardize results related to linguistic evolution or information diffusion. We manually checked on a subsample of clusters that a large proportion of remaining quotes seem to be relevant, while filtered quotes are essentially irrelevant.\rk{fix}}

@@

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/feature_susceptibilities.png}
    \caption{\textbf{Substitution susceptibility:} \rk{fix by replacing "number of synonyms" par "Age of acquisition"} average susceptibility to substitution vs. average feature value of a candidate word for substitution, with 95\% asymptotic confidence intervals.
    The heatmap on the lower-right shows the joint effect of Age of acquisition and Number of phonemes on susceptibility, averaged over the respective single-variable ranges, with sample size (word numbers) in parentheses.
    Without the rather non-significant cells (11 words or less), the heatmap shows no specific trend in one direction or the other.}
    \label{fig:feature-susceptibilities}
\end{figure*}
\medskip
\rk{fix by replacing "number of synonyms" par "Age of acquisition"} Results for this measure are gathered in Fig.~\ref{fig:feature-susceptibilities}. They first show an obvious strong effect of Word frequency: the more frequent a word, the less likely it is to attract substitutions.
Indeed, susceptibility goes from nearly 0.4 for low-frequency words down to 0 for very high-frequency words.
To make things clear, this value of 0.4 means that low-frequency words, when present in a quote undergoing a substitution, are the ones being substituted 40\% of the time on average.

\rk{fix by replacing "number of synonyms" par "Age of acquisition"} The other features --- Age of acquisition, Number of phonemes, Clustering coefficient and Number of synonyms --- do not seem to exhibit any particularly significant effect on susceptibility.
For each of these features, it is indeed possible to draw a constant line which always remains within the respective confidence intervals.
If these variables have an effect, it is by no means as strong as it is for Word frequency.
This is remarkably clear for Clustering coefficient and Number of synonyms, where susceptibility values remain within quite small intervals (respectively [0.09-0.13] and [0.11-0.15]).
We may notice a somewhat marked effect for the highest values of Age of acquisition and Number of phonemes, where the mean susceptibility is almost twice as high as in the rest (respectively 0.19 vs 0.13, and 0.21 vs 0.12).
Keeping in mind the poor statistical significance of this effect, we could still suggest that the longest words and words learned late are more susceptible to substitution.
To further examine this phenomenon, we plotted the two-dimensional map of susceptibility values for these two features (see heatmap at the bottom right of Fig.~\ref{fig:feature-susceptibilities}).
We see that outlier values (the two darkest cells) are both due to cells where the number of items is only slightly above the significance threshold (11 items, while we decided to cut at 10).
If we focus on cells based on at least several dozens of words, values range from 0.11 to 0.22 with little obvious regularity, making it hard to draw any conclusion as regards the direction of an effect.
This confirms the fact that the slight late increases observed for Age of acquisition and Number of phonemes are rather non-significant.

@@

\rk{fix by replacing "number of synonyms" par "Age of acquisition"} All in all, apart from Word frequency and despite some tendencies these results do not allow us to conclude either to a marked effect %or to no effect 
of the selected psycholinguistic features on substitution susceptibility.
We may therefore globally assume that substitution targets are chosen in a more or less uniform way with respect to these features.
